Nodal Discontinuous Galerkin Method for the Euler Equations in GR

### 2018-11-16 Documents/Euler/dgEulerGR.tex
Modified upper limit of pressure to 3*tau
Uncommitted change
Added section RE: linear interpolation error

@@

\subsection{Curvilinear Coordinates}
NOTE: We assume a conformally-flat, time-independent spatial three-metric:
\begin{equation}
    \gamma_{ij}\left(x^{k},t\right)\longrightarrow\psi^{4}\left(x^{k}\right)\,\ol{\gamma_{ii}}\left(x^{k}\right),
\end{equation}
where $\psi\left(x^{k}\right)$ is the conformal factor and $\ol{\gamma}_{ii}$ is the flat-space metric.

\subsubsection{Set of Admissible States}
We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
\begin{equation}
    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF\right)}{1}=\sqrtgm\,\bQ,
\end{equation}
where $\bU$ is given by:
\begin{equation}
    \bU\longrightarrow\begin{pmatrix} D\\ S_{1}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{1}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
\end{equation}
$\bF\left(\bU\right)$ are the fluxes of those conserved quantities:
\begin{equation}
    \bF\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{1}\\ S^{1}\,v_{1}+p\,\delta^{1}_{~1}\\ S^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,v^{1}\,v_{1}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{1}\\ \rho\,h\,W^{2}\,\gamma_{1j}\,v^{1}\,v^{j}+p\\\rho\,h\,W^{2}\,v^{1}-D\,v^{1}\end{pmatrix},
\end{equation}
and $\bQ$ is a source term:
\begin{align}
    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{kj}\,\pd{\gamma_{kj}}{1}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\gamma_{11}}{1}+P^{22}\,\pd{\gamma_{22}}{1}+P^{33}\,\pd{\gamma_{33}}{1}\right] \\0\end{pmatrix}\\
    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{1}+P^{22}\,h_{2}\,\pd{\,h_{2}}{1}+P^{33}\,h_{3}\,\pd{\,h_{3}}{1} \\0\end{pmatrix},
\end{align}
where we have used the fact that $\gamma_{jj}=\left(h_{j}\right)^{2}$. The $P^{kj}$ are components of the pressure tensor:
\begin{equation}
    P^{kj}=S^{k}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{kj}=\gamma^{k\ell}\,S_{\ell}\,v^{j}+p\,\gamma^{k\ell}\,\delta^{j}_{~\ell}=\gamma^{k\ell}\left(S_{\ell}\,v^{j}+p\,\delta^{j}_{~\ell}\right).
\end{equation}
Since the spatial three-metric is diagonal we must have that $\ell=k$. We can therefore simplify further:
\begin{equation}
    P^{kj}=\gamma^{kk}\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\gamma_{kk}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)=\f{1}{\left(h_{k}\right)^{2}}\,\left(S_{k}\,v^{j}+p\,\delta^{j}_{~k}\right)
\end{equation}
For the pressure-tensor sum, we then have:
\begin{equation}\label{Eq:PressureTensorSum}
    P^{kj}\,\p_{1}\,\gamma_{kj}=P^{kk}\,\p_{1}\,\gamma_{kk}=P^{kk}\,\p_{1}\left(h_{k}\right)^{2}=2\,P^{kk}\,h_{k}\,\p_{1}\,h_{k}=\f{2}{h_{k}}\left(S_{k}\,v^{k}+p\right)\,\p_{1}\,h_{k}.
\end{equation}

@@

\subsubsection{Time-Step Derivation/CFL Condition}
We start by integrating both sides over $dx^{1}$ and dividing by the volume, $\Delta V_{i}$:
\begin{equation}
    \f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\pd{\left(\sqrtgm\,\bU_{i}\right)}{t}dx^{1}+\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\pd{\left(\sqrtgm\,\bF\left(\bU_{i}\right)\right)}{1}dx^{1}=\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\sqrtgm\,\bQ_{i}\,dx^{1},
\end{equation}
where:
\begin{equation}
    \Delta V_{i}=\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}dV=\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\sqrtgm\,dx^{1}.
\end{equation}

By defining the cell-average as:
\begin{equation}
    \ol{\bW}_{i}\equiv\f{1}{\Delta V_{i}}\int_{x^{1}_{\imh}}^{x^{1}_{\iph}}\bW_{i}\,dV,
\end{equation}
we have:
\begin{equation}
    \f{d\,\ol{\bU}_{i}}{dt}+\f{1}{\Delta V_{i}}\left.\left(\sqrtgm\,\hat{\bF}\left(\ol{\bU}\right)\right)\right|^{x^{1}_{\iph}}_{x^{1}_{\imh}}=\ol{\bQ}_{i},
\end{equation}
or, using the common notation of the time step being represented as a superscript and the spatial element represented by a subscript:
\begin{equation}
    \ol{\bU}^{n+1}_{i}=\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]+\Delta t_{i}\,\ol{\bQ}^{n}_{i}.
\end{equation}

Now we define a parameter a la \citet{ZS2011b}: $\ve\in\left(0,1\right)$, such that (NOTE: \citet{ZS2011b} set $\ve=1/2$):
\begin{equation}
    \ol{\bU}^{n}_{i}=\ve\,\ol{\bU}^{n}_{i}+\left(1-\ve\right)\ol{\bU}^{n}_{i}.
\end{equation}
We can use the first term to balance out the term in the square brackets and the second term to balance out the source term.

So, we get:
\begin{align}
    \ol{\bU}^{n+1}_{i}&=\ve\left\{\ol{\bU}^{n}_{i}-\f{\Delta t_{i}}{\ve\,\Delta V_{i}}\left[\sqrtgm_{\iph}\,\hat{\bF}^{n}_{\iph}-\sqrtgm_{\imh}\,\hat{\bF}^{n}_{\imh}\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
    &=\ve\left\{\ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right]\right\}+\left(1-\ve\right)\ol{\bU}^{n}_{i}+\Delta t_{i}\,\ol{\bQ}^{n}_{i}\\
    &=\ve\,\ol{\bH}_{1}+\left(1-\ve\right)\ol{\bH}_{2},
\end{align}
where
\begin{equation}
    \ol{\bH}_{1}\equiv \ol{\bU}^{n}_{i}-\eta_{i}\left[\sqrtgm_{\iph}\,\hat{\bF}\left(\ol{\bU}^{n}_{i+1},\ol{\bU}^{n}_{i}\right)-\sqrtgm_{\imh}\,\hat{\bF}\left(\ol{\bU}^{n}_{i},\ol{\bU}^{n}_{i-1}\right)\right],
\end{equation}
\begin{equation}
    \ol{\bH}_{2}\equiv\ol{\bU}^{n}_{i}+\f{\Delta t_{i}}{1-\ve}\,\ol{\bQ}^{n}_{i},
\end{equation}
and
\begin{equation}
    \eta_{i}\equiv\f{\Delta t_{i}}{\ve\,\Delta V_{i}}.
\end{equation}

We proceed by focusing on each term individually, starting with the numerical flux term, $\ol{\bH}_{1}$.

\subsubsection{Numerical flux term}
We have to show that $\ol{\bH}_{1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\ol{\bH}_{1}$:
\begin{align}
    \ol{\bU}^{n}_{i}-\f{\eta_{i}}{2}\Big\{&\sqrtgm_{\iph}\left[\bF\left(\ol{\bU}^{n}_{i+1}\right)+\bF\left(\ol{\bU}^{n}_{i}\right)-\alpha_{\iph}\left(\ol{\bU}^{n}_{i+1}-\ol{\bU}^{n}_{i}\right)\right]\\
    &-\sqrtgm_{\imh}\left[\bF\left(\ol{\bU}^{n}_{i}\right)+\bF\left(\ol{\bU}^{n}_{i-1}\right)-\alpha_{\imh}\left(\ol{\bU}^{n}_{i}-\ol{\bU}^{n}_{i-1}\right)\right]\Big\}\\
    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
    &\hspace{-8em}-\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\bF\left(\ol{\bU}^{n}_{i}\right)+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\bF\left(\ol{\bU}^{n}_{i}\right)\\
    &\hspace{-8em}+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
\end{align}
Now we add and subtract $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\,\ol{\bU}^{n}_{i}$ and $\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\,\ol{\bU}^{n}_{i}$, yielding:
\begin{align}
    &\left(1-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\right)\ol{\bU}^{n}_{i}\\
    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i}\right)\right]\\
    &+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}\left[\ol{\bU}^{n}_{i-1}+\f{1}{\alpha_{\imh}}\bF\left(\ol{\bU}^{n}_{i-1}\right)\right]+\f{1}{2}\,\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}\left[\ol{\bU}^{n}_{i+1}-\f{1}{\alpha_{\iph}}\bF\left(\ol{\bU}^{n}_{i+1}\right)\right].
\end{align}
All of the terms in square brackets are similar to the $\ol{\bH}$ quantities in \citet{Qin2016}, and are therefore in $\cG$. It can easily be seen that the sum of the coefficients is unity. The final condition is that the coefficient of $\ol{\bU}^{n}_{i}>0$, or (recalling that $\eta_{i}=\Delta t_{i}/\left(\ve\,\Delta V_{i}\right)$):
\begin{align}
    1&-\eta_{i}\,\sqrtgm_{\iph}\,\alpha_{\iph}-\eta_{i}\,\sqrtgm_{\imh}\,\alpha_{\imh}>0\implies\eta_{i}\left(\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}\right)<1\\
    &\implies\Delta t_{i}<\f{\ve\,\Delta V_{i}}{\sqrtgm_{\iph}\,\alpha_{\iph}+\sqrtgm_{\imh}\,\alpha_{\imh}}\leq\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}.
\end{align}
Again we want a time-step that is the same for all elements at a given time, so:
\begin{equation}
    \Delta t<\text{min}_{i}\left(\f{\ve\,\Delta V_{i}}{2\,\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)}\right).
\end{equation}

@@

\subsubsubsection{Time-step for Spherical-Polar Coordinates}
For spherical-polar coordinates in 1-D we have that $\Delta V_{i}=1/3\left(r_{\iph}^{3}-r_{\imh}^{3}\right)$, and (assuming $\alpha_{i\pm\f{1}{2}}=1\ \forall\ i$) $\text{max}\left(\sqrtgm_{i\pm\f{1}{2}}\,\alpha_{i\pm\f{1}{2}}\right)=r_{\iph}^{2}$, so:
\begin{align}
    \Delta t&<\text{min}_{i}\left\{\f{\ve\,1/3\left[r_{\iph}^{3}-r_{\imh}^{3}\right]}{2\,r_{\iph}^{2}}\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\f{r_{\imh}^{3}}{r_{\iph}^{3}}\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\left(1-\f{\Delta r_{i}}{r_{\iph}}\right)^{3}\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[1-\left(1+\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}-2\frac{\Delta r_{i}}{r_{\iph}}\right)\left(1-\f{\Delta r_{i}}{r_{\iph}}\right)\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{\iph}\left[\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{3}-3\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}+3\f{\Delta r_{i}}{r_{\iph}}\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,\Delta r_{i}\left[\left(\f{\Delta r_{i}}{r_{\iph}}\right)^{2}-3\left(\f{\Delta r_{i}}{r_{\iph}}\right)+3\right]\right\}.
\end{align}
We know that $\Delta r_{i}/r_{\iph}\in\left[0,1\right]$; the minimum value of the quadratic function in this domain is unity. So, we have that for spherical-polar coordinates:
\begin{equation}
    \Delta t<\f{\ve}{6}\,\text{min}\left(\Delta r_{i}\right).
\end{equation}

@@

\subsubsection{Source term}
For this section we drop the subscript $i$ and the superscript $n$. We have to show that $\ol{\bH}_{2}\in\cG$, where
\begin{equation}
    \ol{\bH}_{2}=\begin{pmatrix}\ol{D}\\ \ol{S}_{1}+\f{\Delta t}{2\left(1-\ve\right)}\ol{P^{kk}\,\pd{\gamma_{kk}}{1}} \\ \ol{\tau}\end{pmatrix},\hspace{1em}\left(\ol{H}_{2}\right)_{1}>0,\hspace{1em}\left(\ol{H}_{2}\right)_{3}+\left(\ol{H}_{2}\right)_{1}>\sqrt{\left(\ol{H}_{2}\right)_{1}\left(\ol{H}_{2}\right)_{1}+\left(\ol{H}_{2}\right)_{2}\left(\ol{H}_{2}\right)^{2}}.
\end{equation}

>>>>

\usepackage{float}

@@

\subsection{Curvilinear Coordinates in 1-D}
NOTE: We assume a conformally-flat, time-independent spatial three-metric:
\begin{equation}
    \gamma_{ij}\left(x^{k},t\right)\longrightarrow\psi^{4}\left(x^{k}\right)\,\ol{\gamma_{ii}}\left(x^{k}\right),
\end{equation}
where $\psi\left(x^{k}\right)$ is the conformal factor and $\ol{\gamma}_{ii}$ is the flat-space metric.

\subsubsection{Set of Admissible States}
We again consider a one-dimensional system of conservation laws, but this time with a curvilinear metric:
\begin{equation}\label{Eq:1DCurvilinearConsLaw}
    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF^{i}\right)}{i}=\sqrtgm\,\bQ,\hspace{1em}\text{(no sum on $i$)},
\end{equation}
where $\bU$ is given by:
\begin{equation}
    \bU\longrightarrow\begin{pmatrix} D\\ S_{j}\\ \tau\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,v_{j}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix}=\begin{pmatrix} \rho\,W\\ \rho\,h\,W^{2}\,\gamma_{jk}\,v^{k}\\ \rho\,W\left(h\,W-1\right)-p\end{pmatrix},
\end{equation}
$\bF^{i}\left(\bU\right)$ are the fluxes in the $x^{i}$-direction of those conserved quantities:
\begin{equation}
    \bF^{i}\left(\bU\right)\longrightarrow\begin{pmatrix}D\,v^{i}\\ S^{i}\,v_{j}+p\,\delta^{i}_{~j}\\ S^{i}-D\,v^{i}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{i}\\ \rho\,h\,W^{2}\,v^{i}\,v_{j}+p\,\delta^{i}_{~j}\\\rho\,h\,W^{2}\,v^{i}-D\,v^{i}\end{pmatrix}=\begin{pmatrix}\rho\,W\,v^{i}\\ \rho\,h\,W^{2}\,\gamma_{jk}\,v^{i}\,v^{k}+p\,\delta^{i}_{~j}\\\rho\,h\,W^{2}\,v^{i}-D\,v^{i}\end{pmatrix},
\end{equation}
and $\bQ$ is a source term:
\begin{align}
    \bQ\longrightarrow\begin{pmatrix}0\\\f{1}{2}\,P^{ik}\,\pd{\,\gamma_{ik}}{j}\\0\end{pmatrix}&=\begin{pmatrix}0\\ \f{1}{2}\left[P^{11}\,\pd{\,\gamma_{11}}{j}+P^{22}\,\pd{\,\gamma_{22}}{j}+P^{33}\,\pd{\,\gamma_{33}}{j}\right] \\0\end{pmatrix}\\
    &=\begin{pmatrix}0\\ P^{11}\,h_{1}\,\pd{\,h_{1}}{j}+P^{22}\,h_{2}\,\pd{\,h_{2}}{j}+P^{33}\,h_{3}\,\pd{\,h_{3}}{j} \\0\end{pmatrix},
\end{align}
where we have used the fact that $\gamma_{kk}=\left(h_{k}\right)^{2}$. The $P^{ik}$ are components of the pressure tensor:
\begin{equation}
    P^{ik}=S^{i}\,v^{k}+p\,\gamma^{ik}=\gamma^{i\ell}\,S_{\ell}\,v^{k}+p\,\gamma^{ik}=\gamma^{i\ell}\,S_{\ell}\,v^{k}+p\,\gamma^{i\ell}\,\delta^{k}_{~\ell}=\gamma^{i\ell}\left(S_{\ell}\,v^{k}+p\,\delta^{k}_{~\ell}\right).
\end{equation}
Since the spatial three-metric is diagonal the only non-zero term is that with $\ell=i$. We can therefore simplify further:
\begin{equation}
    P^{ik}=\gamma^{ii}\left(S_{i}\,v^{k}+p\,\delta^{k}_{~i}\right)=\f{1}{\gamma_{ii}}\,\left(S_{i}\,v^{k}+p\,\delta^{k}_{~i}\right),\hspace{1em}\text{(no sum on $i$)}.
\end{equation}
For the source-term sum we then have:
\begin{equation}\label{Eq:PressureTensorSum}
    Q_{j}=\f{1}{2}\,P^{ik}\,\p_{j}\,\gamma_{ik}=\f{1}{2}\,P^{kk}\,\p_{j}\,\gamma_{kk}=\f{1}{2}\,P^{kk}\,\p_{j}\left(h_{k}\right)^{2}=P^{kk}\,h_{k}\,\p_{j}\,h_{k}.
\end{equation}

@@

\subsubsection{Time-Step Derivation/CFL Condition}
We start by integrating both sides of \eqref{Eq:1DCurvilinearConsLaw} over $dx^{i}$ and dividing by the volume of the $K^{th}$ element, $\Delta V_{K}$ (recalling that there is no sum on $i$):
\begin{equation}
    \f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\pd{\left(\sqrtgm\,\bU\right)}{t}dx^{i}+\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\pd{\left(\sqrtgm\,\bF^{i}\left(\bU\right)\right)}{i}dx^{i}=\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\sqrtgm\,\bQ\,dx^{i},
\end{equation}
where:
\begin{equation}
    \Delta V_{K}=\int_{x^{i}_{L}}^{x^{i}_{H}}dV=\int_{x^{i}_{L}}^{x^{i}_{H}}\sqrtgm\,dx^{i}.
\end{equation}

By defining the cell-average as:
\begin{equation}
    \bW_{K}\equiv\f{1}{\Delta V_{K}}\int_{x^{i}_{L}}^{x^{i}_{H}}\bW\,dV,
\end{equation}
we have:
\begin{equation}
    \f{d\,\bU_{K}}{dt}+\f{1}{\Delta V_{K}}\left.\left(\sqrtgm\,\hat{\bF}\left(\bU\right)\right)\right|^{x^{i}_{H}}_{x^{i}_{L}}=\bQ_{K}.
\end{equation}
Now, using the common notation of the time step being represented as a superscript $n$:
\begin{equation}
    \bU^{n+1}_{K}=\bU^{n}_{K}-\f{\Delta t^{n}_{K}}{\Delta V_{K}}\left[\sqrtgm_{H}\,\hat{\bF}^{n}_{H}-\sqrtgm_{L}\,\hat{\bF}^{n}_{L}\right]+\Delta t^{n}_{K}\,\bQ^{n}_{K}.
\end{equation}

Now we define a parameter a la \citet{ZS2011b}: $\ve\in\left(0,1\right)$, such that (NOTE: \citet{ZS2011b} set $\ve=1/2$):
\begin{equation}
    \bU^{n}_{K}=\ve\,\bU^{n}_{K}+\left(1-\ve\right)\bU^{n}_{K}.
\end{equation}
We can use the first term to balance out the term in the square brackets and the second term to balance out the source term.

So, we get:
\begin{align}
    \bU^{n+1}_{K}&=\ve\left\{\bU^{n}_{K}-\f{\Delta t^{n}_{K}}{\ve\,\Delta V_{K}}\left[\sqrtgm_{H}\,\hat{\bF}^{n}_{H}-\sqrtgm_{L}\,\hat{\bF}^{n}_{L}\right]\right\}+\left(1-\ve\right)\bU^{n}_{K}+\Delta t^{n}_{K}\,\bQ^{n}_{K}\\
    &=\ve\left\{\bU^{n}_{K}-\eta^{n}_{K}\left[\sqrtgm_{H}\,\hat{\bF}\left(\bU^{n}_{K+1},\bU^{n}_{K}\right)-\sqrtgm_{L}\,\hat{\bF}\left(\bU^{n}_{K},\bU^{n}_{K-1}\right)\right]\right\}+\left(1-\ve\right)\bU^{n}_{K}+\Delta t^{n}_{K}\,\bQ^{n}_{K}\\
    &=\ve\,\bH_{K,1}+\left(1-\ve\right)\bH_{K,2},
\end{align}
where
\begin{equation}
    \bH_{K,1}\equiv \bU^{n}_{K}-\eta^{n}_{K}\left[\sqrtgm_{H}\,\hat{\bF}\left(\bU^{n}_{K+1},\bU^{n}_{K}\right)-\sqrtgm_{L}\,\hat{\bF}\left(\bU^{n}_{K},\bU^{n}_{K-1}\right)\right],
\end{equation}
\begin{equation}
    \bH_{K,2}\equiv\bU^{n}_{K}+\f{\Delta t^{n}_{K}}{1-\ve}\,\bQ^{n}_{K},
\end{equation}
and
\begin{equation}
    \eta^{n}_{K}\equiv\f{\Delta t^{n}_{K}}{\ve\,\Delta V_{K}}.
\end{equation}

We proceed by focusing on each term individually, starting with the numerical flux term, $\bH_{K,1}$.

\subsubsection{Numerical flux term}
We have to show that $\bH_{K,1}\in\cG$. We again we use the Local-Lax-Friedrichs flux, \eqref{Eq:LLF}, yielding for $\bH_{K,1}$:
\begin{align}
    \bU^{n}_{K}-\f{\eta^{n}_{K}}{2}\Big\{&\sqrtgm_{H}\left[\bF\left(\bU^{n}_{K+1}\right)+\bF\left(\bU^{n}_{K}\right)-\alpha^{n}_{H}\left(\bU^{n}_{K+1}-\bU^{n}_{K}\right)\right]\\
    &-\sqrtgm_{L}\left[\bF\left(\bU^{n}_{K}\right)+\bF\left(\bU^{n}_{K-1}\right)-\alpha^{n}_{L}\left(\bU^{n}_{K}-\bU^{n}_{K-1}\right)\right]\Big\}\\
    &\hspace{-10em}=\left(1-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\right)\bU^{n}_{K}\\
    &\hspace{-8em}-\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\bF\left(\bU^{n}_{K}\right)+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\bF\left(\bU^{n}_{K}\right)\\
    &\hspace{-8em}+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K-1}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K-1}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K+1}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K+1}\right)\right].
\end{align}
Now we add and subtract $\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\,\bU^{n}_{K}$ and $\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\,\bU^{n}_{K}$, yielding:
\begin{align}
    &\left(1-\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\right)\bU^{n}_{K}\\
    &+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K}\right)\right]\\
    &+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}\left[\bU^{n}_{K-1}+\f{1}{\alpha^{n}_{L}}\bF\left(\bU^{n}_{K-1}\right)\right]+\f{1}{2}\,\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}\left[\bU^{n}_{K+1}-\f{1}{\alpha^{n}_{H}}\bF\left(\bU^{n}_{K+1}\right)\right].
\end{align}
All of the terms in square brackets are similar to the $\bH_{K}$ quantities in \citet{Qin2016}, and are therefore in $\cG$. It can easily be seen that the sum of the coefficients is unity. The final condition is that the coefficient of $\bU^{n}_{K}>0$, or (recalling that $\eta^{n}_{K}=\Delta t_{K}/\left(\ve\,\Delta V_{K}\right)$):
\begin{align}
    1&-\eta^{n}_{K}\,\sqrtgm_{H}\,\alpha^{n}_{H}-\eta^{n}_{K}\,\sqrtgm_{L}\,\alpha^{n}_{L}>0\implies\eta^{n}_{K}\left(\sqrtgm_{H}\,\alpha^{n}_{H}+\sqrtgm_{L}\,\alpha^{n}_{L}\right)<1\\
    &\implies\Delta t^{n}_{K}<\f{\ve\,\Delta V_{K}}{\sqrtgm_{H}\,\alpha^{n}_{H}+\sqrtgm_{L}\,\alpha^{n}_{L}}\leq\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha^{n}_{K\pm\f{1}{2}}\right)}.
\end{align}
Again we want a time-step that is the same for all elements at a given time, so:
\begin{equation}
    \Delta t^{n}<\text{min}_{K}\left(\f{\ve\,\Delta V_{K}}{2\,\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha^{n}_{K\pm\f{1}{2}}\right)}\right).
\end{equation}

@@

\subsubsubsection{Time-step for Spherical-Polar Coordinates}
For spherical-polar coordinates in 1-D we have that $\Delta V_{K}=1/3\left(r_{H}^{3}-r_{L}^{3}\right)$, and (assuming $\alpha_{K\pm\f{1}{2}}=1\ \forall\ i$) $\text{max}\left(\sqrtgm_{K\pm\f{1}{2}}\,\alpha_{K\pm\f{1}{2}}\right)=r_{H}^{2}$, so:
\begin{align}
    \Delta t&<\text{min}_{i}\left\{\f{\ve\,1/3\left[r_{H}^{3}-r_{L}^{3}\right]}{2\,r_{H}^{2}}\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\f{r_{L}^{3}}{r_{H}^{3}}\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\left(1-\f{\Delta r_{i}}{r_{H}}\right)^{3}\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[1-\left(1+\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}-2\frac{\Delta r_{i}}{r_{H}}\right)\left(1-\f{\Delta r_{i}}{r_{H}}\right)\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,r_{H}\left[\left(\f{\Delta r_{i}}{r_{H}}\right)^{3}-3\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}+3\f{\Delta r_{i}}{r_{H}}\right]\right\}\\
    &=\text{min}_{i}\left\{\f{\ve}{6}\,\Delta r_{i}\left[\left(\f{\Delta r_{i}}{r_{H}}\right)^{2}-3\left(\f{\Delta r_{i}}{r_{H}}\right)+3\right]\right\}.
\end{align}
We know that $\Delta r_{i}/r_{H}\in\left[0,1\right]$; the minimum value of the quadratic function in this domain is unity. So, we have that for spherical-polar coordinates:
\begin{equation}
    \Delta t<\f{\ve}{6}\,\text{min}\left(\Delta r_{i}\right).
\end{equation}

@@

\subsubsection{Source term}
For this section we drop the subscript $K$ and the superscript $n$ (but keep in mind that all quantities are still cell-averages). We have to show that $\bH_{2}\in\cG$, where
\begin{equation}
    \bH_{2}=\begin{pmatrix}D\\ S_{j}+\f{\Delta t}{1-\ve}\,Q_{j} \\ \tau\end{pmatrix},\hspace{1em}\left(H_{2}\right)_{1}>0,\hspace{1em}\left(H_{2}\right)_{5}+\left(H_{2}\right)_{1}>\sqrt{\left(H_{2}\right)_{1}\left(H_{2}\right)_{1}+\left(H_{2}\right)_{j}\left(H_{2}\right)^{j}}.
\end{equation}
